### 2014-03-01 paper/retrofit.tex
More notation fixes.

\and
\inferrule[T-ref]
{ }
{| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}
{| fresh ta |}

\and
\inferrule[T-deref]
{ }
{| conf tS (!ta) -> conf tS (ap tS ta) |}

\and
\inferrule[T-ass]
{ |(ta, tv) in tS| }
{| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = iS [ mapsto id' nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

>>>>

\and
\inferrule[T-ref]
{ | ap fresh ta | }
{| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}

\and
\inferrule[T-deref]
{ |(ta, tv) in tS| }
{| conf tS (!ta) -> conf tS (tv) |}

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = iS [ mapsto id' nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|ap fresh id'|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}
